Scaling continuous reinforcement learning up

### 2018-10-20 paper/main.tex
Pap

\paragraph{Learning rates scalings}
\TODO{More on that later. In noisy setups we may need $\frac{1}{\deltat^\frac{3}{2}}$ for the last term of the loss.}
Actual loss we minimize on both $\theta$ and $\phi$
\begin{equation}
	\E_{s \sim \rho^\pi, a \sim \pi}\left[\delta^A_{\theta, \phi}(s, a)^2\right] +
	\E_{s \sim \rho^\pi, a \sim \pi}\left[\delta^\text{norm}_{\theta}(s, a)^2\right] +
	+ \frac{1}{\deltat}\E_{s \sim \rho^\pi}\left[\delta^\text{mean}_{\theta}(s)^2\right]
\end{equation}
Learning rate on $\phi$ and $b$ are of order $\deltat$, learning rate on $\theta$ is of order $\deltat^2$. This is to have gradients moving of approximately $\sqrt{dt}

>>>>

\paragraph{Learning rates scalings}
\TODO{More on that later. I am not sure if we should have a $\frac{1}{\deltat}$
	or a $\frac{1}{\deltat^\frac{3}{2}}$ in front of the mean normalization
term. My bet is $\frac{1}{\deltat^\frac{3}{2}}$}.
Actual loss we minimize on both $\theta$ and $\phi$
\begin{equation}
	\E_{s \sim \rho^\pi, a \sim \pi}\left[\delta^A_{\theta, \phi}(s, a)^2\right] +
	\E_{s \sim \rho^\pi, a \sim \pi}\left[\delta^\text{norm}_{\theta}(s, a)^2\right] +
	+ \frac{1}{\deltat^\frac{3}{2}}\E_{s \sim \rho^\pi}\left[\delta^\text{mean}_{\theta}(s)^2\right].
\end{equation}
Learning rates on $\phi$ and $b$ are of order $\deltat$, learning rate on $\theta$ is of order $\deltat^2$. This is to have parameters
moving by a distance of order $\sqrt{\deltat}$ per iteration.
